Question 2: Does average cost of a heart failure procedure affect mortality rate?
Load all the files and view the hospital dataset
<!-- REFERENCE  -->
```{r}
library(tidyverse)
hospitals <- read_csv("https://raw.githubusercontent.com/36-SURE/36-SURE.github.io/main/data/hospitals.csv")

hospitals
View(hospitals)

```
Look at the different column names in the hospitals dataset.
```{r}
names(hospitals)
```
Change columns names to improve naming styles
```{r}
hospitals_named <- hospitals |>
  rename(heart.failure.cost = "Procedure.Heart Failure.Cost") |>
  mutate(Rating.Mortality = factor(Rating.Mortality, levels = c("Below", "Same", "Above")))

View(hospitals_named)
```

Code to create 3 side by side box plots of heart failure procedure costs based on the hospital's mortality rate based on the national average mortality rate (which is same). 

```{r}
hospitals_named |>
  filter(Rating.Mortality %in% c("Above", "Same", "Below")) |>
  ggplot(aes(x = heart.failure.cost, y = Rating.Mortality)) +
  geom_boxplot(fill = "lightblue", color = "black") + 
  labs(
    x = "Cost of Heart Failure Procedure",
    y = "Mortality Rating Compared to National Average",
    title = "Heart Failure Procedure Costs Related to Mortality Rate", 
    caption = "Data from CORGIS Dataset Project"
  ) + 
  theme_bw() +
  theme(
    legend.position = "bottom",
    strip.background = element_blank(),
    plot.title = element_text(hjust = 0.5, face = "bold")
  )

```
attempt
```{r}
hospitals |>
  ggplot(aes(x = "Procedure.Heart Failure.Cost")) +
  geom_boxplot(fill = "red", color = "white")
```

